Risk Perceptions for Wearable Devices

### 2015-03-07 tex-inputs/results-demographics.tex
More dead orphans

Participants' responses were correlated with demographic factors. The biggest predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}. A Spearman correlation yielded a statistically significant effect between average IUIPC scores with the VUR ($\rho=0.446$, $p<0.0005$), which suggest responses to questions were mostly based on privacy preferences. Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$). We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more protective of their privacy~\cite{varian2005demographics}.

>>>>

The biggest demographic predictor of participants' decisions to rate a scenario as very upsetting was their self-reported level of general privacy concerns, as determined by the IUIPC scale~\cite{malhotra2004internet}. A Spearman correlation yielded a statistically significant effect between average IUIPC scores and VUR ($\rho=0.446$, $p<0.0005$), which suggests responses to questions were mostly based on privacy preferences. Additionally, we observed that age was a significant predictor of VUR ($\rho=0.121$, $p<0.0005$). We suspect that the effect of age is due to the significant correlation between age and IUIPC scores ($\rho=0.188$, $p<0.0005$); others have observed that older individuals tend to be more privacy protective~\cite{varian2005demographics}.

### 2015-03-07 tex-inputs/results-openended.tex
More dead orphans

%!TEX root = ../paper.tex
\subsection{Self-Reported Concerns for Wearables}
We also wanted to capture the participants' general reactions to wearable devices as a whole. To do this, we asked the participants the following open-ended question:

@@

Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Most are related to privacy and security, but this self-report gives a sense of what broad categories of concerns are most relevant to users. This can be used to guide research in unexplored use cases.

In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware). Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions which cause car accidents (Safety), resulting changes in social behaviors, such as dependencies on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\% \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Social Impact &	157 & 8.80\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{A table listing the self-reported most common risks associated with owning a wearable device.}
\label{openresponses}
\end{center}
\end{table}

>>>>

%!TEX root = ../paper.tex
\subsection{Open-Ended Concerns for Wearables}
We captured participants' general reactions to wearable devices as a whole by asking the following open-ended question:

@@

Table \ref{openresponses} shows common user concerns related to wearable devices. Appendix \ref{sec:coding} details the responses categorized in each coding label. Most are related to privacy and security, but this open-ended data gives a sense of what broad categories of concerns are most relevant to users. This can be used to guide research in unexplored use cases.

In addition to privacy and security in the general sense, significant concerns included being unaware of what the device is collecting, doing, or which information it is using (Being Unaware). Other concerns were orthogonal to privacy, such as long-term health effects caused from wearing the device such as cancer from EMF waves (Health), safety hazards from wearing the device, such as distractions that cause car accidents (Safety), resulting changes in social behaviors, such as dependence on devices or spending less time with loved ones (Social Impact), the high financial cost of buying, replacing, or caring for the device (Financial).

\begin{table}[t]
\begin{center}
\begin{tabular}{|l|r|r|}
\hline
Concern &  Responses &  Frequency   \\
\hline
Privacy & 452 & 25.32\% \\
Being Unaware & 275 & 15.40\% \\
%Unaware Use & 167 & (9.36\%)\\
%Unaware Collection & 64 & (3.59\%)\\
%Unaware Access & 44 & (2.46\%)\\
Health Risk & 191 & 10.70\%\\
Safety & 185 & 10.42\%\\
Social Impact &	157 & 8.80\%\\
Financial Cost & 151 & 8.46\%\\
Security &	144 & 8.07\%\\
Accidental Sharing &	69 & 3.87\%\\
Miscellaneous &	57 & 3.19\%\\
None	& 51 & 2.86\%\\
Social Stigma &	39 & 2.18\%\\
False Information & 33 & 1.85\%\\
Don't know & 31 & 1.74\%\\
Aesthetics 	& 19 & 1.06\%\\
Don't care 	& 11 & 0.62\%\\
\hline
\end{tabular}
\caption{The most common open-ended risks associated with owning a wearable device.}
\label{openresponses}
\end{center}
\end{table}
